Category-based and location-based volitional covert attention affect memory at different timescales

### 2023-04-16 paper/main.tex
more formatting fixes to address editor requests

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{hyperref}
\usepackage[sort, square, numbers, compress]{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\usepackage{soul}
\usepackage{setspace,caption}
\doublespacing
\captionsetup[figure]{labelsep=period,labelfont=it,justification=justified,
 singlelinecheck=false,font=doublespacing}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\linenumbers

@@

We ran a total of 53 participants across two experimental conditions
(Fig.~\ref{fig:paradigm}). The two conditions differed in how often we cued
participants to change the focus of their attention. All code and documentation
pertaining to our experiment and analyses, along with the experimental stimuli
and data, may be downloaded from
\url{http://www.github.com/ContextLab/attention-memory-task}. All methods were
performed in accordance with the relevant duidelines and regulations, and our
experimental protocol was approved by the Committee for the Protection of Human
Subjects at Dartmouth College.

@@

\bibliographystyle{apacite}
\bibliography{CDL-bibliography/cdl}

>>>>

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
%\usepackage{apacite}
\usepackage{hyperref}
\usepackage[sort, square, numbers, compress]{natbib}
%\usepackage[english]{babel}
%\usepackage[backend=biber, natbib=true, style=numeric, sorting=true]{biblatex}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\usepackage{soul}
\usepackage{setspace,caption}
\doublespacing
\captionsetup[figure]{labelsep=period,labelfont=it,justification=justified,
 singlelinecheck=false,font=doublespacing}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\linenumbers

@@

We ran a total of 53 participants across two experimental conditions
(Fig.~\ref{fig:paradigm}). The two conditions differed in how often we cued
participants to change the focus of their attention. All code and documentation
pertaining to our experiment and analyses, along with the experimental stimuli
and data, may be downloaded from
\url{http://www.github.com/ContextLab/attention-memory-task}. All methods were
performed in accordance with the relevant guidelines and regulations, and our
experimental protocol was approved by the Committee for the Protection of Human
Subjects at Dartmouth College.

@@

\bibliographystyle{naturemag}
\bibliography{CDL-bibliography/cdl}
